---
title: "Clients Pain Point Summary"
author: George Shang
format: 
  pdf: 
    fontfamily: times
editor: visual
---

```{r setup, include=FALSE}
library(mosaic)
library(ggplot2)
library(ggformula)
```

# Category of Issues:

### Capital:

These are issues regarding sourcing capital and funding. Clients have difficulty or want support in finding sources for funding and capital for their businesses, such as crowd sourcing. This could also include helping them understand what their funding options are and what the costs are. 

### Marketing:

These are issues regarding marketing, growing the business, getting more clients or customers, or having a bigger online presence. Clients are thinking about ways to grow and expand their business, whether that’s through online presence or through marketing efforts.

### Management:

These are issues regarding the structuring, management, and organization of the business. The issues could be a variety of things, such as hiring more employees, a strategy going forward, brand story, or pitching. There could also be support needed for financial management, from cash flow statements to pricing.

### Planning:

These are the issues for clients that are just starting out and they are not quite sure where to start. This is different than general management issues as these clients, and the issues mostly lies upon "where do I get started", how to secure the first few customers, and what should the business be about.

### Legal:

These are issues regarding certifications or needing legal guidance. Clients need help with getting certain disability/minority certifications or obtaining legal status or “legitimizing” their business. These could range from FDA approval, forming an LLC, to securing a patent.

### Network:

These are issues which needs networking and connections from WBDC. Clients who come from a minority background needs a bigger network, connection to resources, or referral to other individuals and events.

# Percentages of Each Issue by Category:

```{r, echo = FALSE}
df = read.csv("filtered-data.csv")

percentages = df |>
  select(capital:network) |>
  colMeans() * 100

data = data.frame(category = names(percentages), 
                  percentage = as.numeric(percentages)) |>
  arrange(desc(percentage)) |>
  mutate(category = factor(category, levels = category))
  
data |>
  gf_col(percentage ~ category, fill = "orange", color = "darkmagenta") |>
  gf_labs(title = "Percentage of Each Category",
          x = "Category",
          y = "Percentage")
```


